---
title: "Fun"
author: "Chris Shockley"
date: "May 9, 2018"
output: html_document
---

---
title: "MARGIN PROJECT"
author: "Chris Shockley"
date: "April 30, 2018"
output:
  html_document: default
  word_document: default
  pdf_document: default
---
# Table of contents
1. [Introduction](#testing 123)
2. [Methodology](#paragraph1)
3. [Project](#paragraph2)
    1. [Data Cleaning](#Data_cleaning)
    1. [Creating Industry Vectors](#code)
    2. [Randomization](#for loop)
    3. [Confidence Intervals](#anova analysis)
4. [Conclusion](#conclusion_of_Null)

## Introduction <a name="testing_123"></a>
This Analysis deals with the question as to whether or not there is a difference a statistcal difference between quality of sleep and smoking cigarrettes.  The data set used is the NHANES data set.  

```{r}
library(NHANES)
library(ggplot2)
library(dplyr)

```

```{r}
names(NHANES)
df <- NHANES[,c("SleepHrsNight", "SmokeNow", "Age")]
df <- na.omit(df)

df_smoke <- df[df$SmokeNow == "Yes",]
df_nosmoke <- df[df$SmokeNow == "No",]

t.test(df_smoke$SleepHrsNight, df_nosmoke$SleepHrsNight)

summary(lm(df$SleepHrsNight ~ ., df))
summary(lm(hwy~., mpg))

```

